---
title: "Preprocess data, match IDs, compensate participants"
author: "Bria Long"
date: "2025-03-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(jsonlite)
library(tidyverse)
library(lubridate)
```

THIS IS IDENTIFIABLE DATA AND NOT SHAREABLE.
These data files need to be updated every so often
```{r}
load(here::here('data/preprocessed/all_children_identifiable2025-03-11.RData'))

all_children <- all_children |> 
  mutate(child__age_rounded=round(age_in_days/10)*10) # rounding to nearest tenth to de-identify
```

Now for participant we have IDs for
```{r}
roar_data_after_fix <- read_csv(here::here('data/roar_datafiles/vocab-garden-trials-04262024-v2.csv')) %>%
  full_join(read_csv(here::here('data/roar_datafiles/vocab-garden-trials-04262024-v1.csv'))) %>%
  full_join(read_csv(here::here('data/roar_datafiles/vocab-garden-trials-04262024-08262024.csv')))
```

Load manually matched data
```{r}
load(file=here::here('data/preprocessed/manually_matched_data_before_122823.RData'))

matched_with_age <- matched %>%
  rename(child_id_incorrect = child_id) %>%
  rename(child_id = child_id_lookit) %>%
  left_join(all_children %>% select(child_id, child_global_id, child__age_rounded)) %>% # add back age
  distinct(child_id_incorrect, child_id, child_global_id, child__age_rounded) # keeping distinct entry in case participant tried to participate multiple times in the same day
```

Get matched children from after the bug fix 
```{r}
matched_children_all <- all_children %>%
  filter(!is.na(start_timestamp)) %>% # had a timestamp
  mutate(day = day(start_timestamp), month = month(start_timestamp)) %>%
  filter(child_id != 'cXAAAP') %>% # test participant
  filter(consent == 'accepted') %>% # true by definition
  mutate(lookit_duration = difftime(ymd_hms(end_timestamp), ymd_hms(start_timestamp), units='mins')) %>%
  group_by(parent_id, child_id) %>%
  mutate(max_duration = max(lookit_duration)) %>%
  filter(lookit_duration == max_duration) %>% # only get one session per child, sometimes they attempted twice
  ungroup() %>%
  mutate(after_fix = ymd_hms(start_timestamp) > ymd("2023-12-27")) %>%
  distinct(child_id, child_global_id, parent_id, completed, lookit_duration, start_timestamp, child__age_rounded, after_fix, session_id)

matched_children_after_fix <- matched_children_all %>%
  filter(after_fix == TRUE) %>% 
  select(child_id, child_global_id, child__age_rounded, session_id)
```

All raw roar data with child_id and age
```{r}
pre_fix <- read_csv(here::here('data/roar_datafiles/vocab-garden-trials-122723.csv')) %>%
  mutate(tech_error = TRUE) %>%
  right_join(matched_with_age, by=c('user.assessmentPid'='child_id_incorrect')) 

all_garden_roar_data_with_age = roar_data_after_fix %>%
  rowwise() %>%
  mutate(tech_error = FALSE) %>%
  rename(child_id = user.assessmentPid, session_id = sessionId) %>%
  right_join(matched_children_after_fix) %>% 
  full_join(pre_fix)%>%
  filter(assessment_stage == 'test_response')
```
Remove items which were displayed incorrectly to a few participants
```{r}
low_counts <- all_garden_roar_data_with_age |>
  group_by(targetWord) |>
  mutate(num_participants = n()) |>
  filter(num_participants < 5) |> # correct trial types should have at least 10 participants 
  select(-starts_with("scores."), -child_global_id, -starts_with("user.")) |>
  ungroup()

summarized_low_counts <- low_counts |>
  summarize(n = n(), child_ids = list(child_id), .by=c("targetWord", "itemSource"))

filtered_garden_roar_data_with_age <- all_garden_roar_data_with_age |>
  filter(!(targetWord %in% summarized_low_counts$targetWord))
```

# Creating participant-level summary sheet

Describing exclusion criteria
```{r}
# Participants for who data could not be recovered because of tech error
tech_error_no_data <- matched_children_all %>% 
  filter(after_fix==FALSE) %>%
  filter(!child_id %in% pre_fix$child_id) %>%
  mutate(pc = NA, num_trials = NA, tech_error = TRUE) %>%
   mutate(start_time = as.Date(start_timestamp)) %>%
  select(child_id, child_global_id, num_trials, pc, tech_error, start_time, child__age_rounded)

# Participants who did not get past the practice trials
did_not_start_task <- matched_children_all %>% 
  filter(after_fix==TRUE) %>%
  filter(!child_id %in% all_garden_roar_data_with_age$child_id) %>%
  mutate(pc = NA, num_trials = NA, tech_error = FALSE, did_not_start=TRUE) %>%
  mutate(start_time = as.Date(start_timestamp)) %>%
  select(child_id, child_global_id, num_trials, pc, did_not_start, start_time, child__age_rounded)
```

Summarizing data for the participant level
```{r}
roar_summary_by_child_id <- filtered_garden_roar_data_with_age  %>%
  filter(!is.na(child_global_id)) %>%
  group_by(child_global_id, child_id) %>%
  mutate(tech_error = FALSE) %>%
  mutate(pc = round(mean(correct), 4), num_trials = length(unique(trialId))) %>%
  full_join(tech_error_no_data) %>%
  full_join(did_not_start_task) %>%
  mutate(VO_exclude_notes = case_when(
    tech_error==TRUE ~ "tech error - no data",
    did_not_start==TRUE ~ "did not start the study",
    TRUE ~ ""
  ), VO_exclude = ifelse(VO_exclude_notes == "", 0, 1),
      response__date_created = format(start_time, "%Y-%m-%d %H:%M"),
  age_years = round(child__age_rounded/365, 4)) |>
  # Pivoting wider so that trials are at a participant level 
  pivot_wider(id_cols=c(child_global_id, child_id, age_years, VO_exclude, VO_exclude_notes, response__date_created, pc, num_trials), names_from="targetWord", values_from="correct", names_glue = "{targetWord}_trial")
  
# join in garden ids
garden_ids <- read_csv(here::here("data/roar_datafiles/gardenP1-ids_7visualvocab_identifiable.csv"))
roar_summary_with_garden_ids <- roar_summary_by_child_id |>
  ungroup() |>
  left_join(garden_ids |> select(hashid_7visualvocab, child__garden_id), by=c("child_id"="hashid_7visualvocab")) |>
  rename(child__hashed_id=child_id) |>
  relocate(child__garden_id, .before = VO_exclude) |>
  relocate(age_years, .before=VO_exclude) |>
  select(-child_global_id, -NA_trial) 

write_csv(roar_summary_with_garden_ids, file=here::here('data/GARDEN-phase1_study-visualvocab_data.csv'))

data_dictionary <- tibble(Variable = colnames(roar_summary_with_garden_ids)) |> 
  rowwise() |>
  mutate(description = ifelse(grepl("_trial$", Variable), paste("Performance on picture-matching trial where the correct choice was", strsplit(Variable, "_")[[1]][1], "from among four images"), NA))
write_csv(data_dictionary, file=here::here('GARDEN_VO_module_data_dictionary_03112025.csv'))

```

Creating additional trial level file
```{r}
roar_summary_trial_level <- all_garden_roar_data_with_age |>
  rename(child__hashed_id=child_id) |>
  select(child__hashed_id,correct, child__age_rounded, targetWord, answerWord, trial_index, rt, options, itemSource) |>
  left_join(roar_summary_with_garden_ids |> select(child__hashed_id, child__garden_id, pc))
write_csv(roar_summary_trial_level, file=here::here('data/output/trial_level_summary.csv'))
```

Plot descriptives
```{r}
library(ggthemes)
ggplot(roar_summary_by_child_id, aes(x=age_years, y=pc, size=num_trials)) +
  geom_point(alpha=.4) +
  theme_few() +
  ylab("Percent correct") +
  xlab("Age in years") +
  geom_smooth(aes(weight=num_trials)) +
  theme(legend.position='none')
```

Save out de-identified raw data file: removing global ID and identifiable age in days
```{r}
write_csv(all_garden_roar_data_with_age |> select(-child_global_id, -age_in_days), file=here::here('data/output/all_garden_roar_data_with_age.csv'))
```



